Creating an Evolution Simulator for Protein Low Complexity Regions and Attempting to Utilize it for an Approximate Bayesian Computation

### 2023-03-30 beap_pres_dec2022/beap_pres_dec.tex
updates
Updates to bus presentation, almost done script

	\begin{frame}{What we Did in this Study}
		\begin{itemize}
			\item 
		\end{itemize}
	\end{frame}

@@

	\begin{frame}{LCR Simulator Overall Process}
		\begin{center}
			\begin{enumerate}
				\item Random Protein Sequence \newline	
				GGAGGGAQ \newline		
				mutation rate = 0.14
				indel rate = 0.14  \newline\pause

@@

	\begin{frame}{LCR Simulator Results}

	\begin{frame}{LCR Simulator Results 2}

	\begin{frame}{LCR Simulator Results 3}

	\begin{frame}{LCR Simulator Results 4}

@@

	%Slide 14 - Maybe to this slide - Maybe throw in extra slides for reference

	%For my Concluding slides, I will talk about things such as 
	%SLIDE 16%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\section{Future Work}
	\begin{frame}{Future Work}

>>>>

	\begin{frame}{What we Did in this Study}
		\begin{itemize}
			\item Utilized \texttt{C++} to build an evolution simulator which altered protein sequences via point mutations, insertions, and deletions \newline
			\item Tested the simulator with various insertion/deletion rates and mutation rates \newline
			\item Attempted to program an ABC-MCMC in \texttt{C++} using the evolution simulator as an important step in the algorithm, in order to estimate parameters like mutation and indel rates.
		\end{itemize}
	\end{frame}

@@

	\begin{frame}{LCR Simulator Overall Process}
		\begin{center}
			\begin{enumerate}
			\item mutation rate = 0.14
				indel rate = 0.14 \newline
				Random Protein Sequence \newline	
				GGAGGGAQ \newline\pause

@@

	\begin{frame}{LCR Simulator Results}
		\includegraphics[height=6cm, width=\textwidth]{im0.01-0.1-0.5.jpeg}
	\end{frame}

	\begin{frame}{LCR Simulator Results 2}
		\includegraphics[height=7cm, width=\textwidth]{im1-2-10.jpeg}
	\end{frame}

	\begin{frame}{LCR Simulator Results 3}
		\includegraphics[height=7cm, width=\textwidth]{m0.01-0.1-0.5.jpeg}
	\end{frame}

	\begin{frame}{LCR Simulator Results 4}
		\includegraphics[height=7cm, width=\textwidth]{m1-2-10.jpeg}
	\end{frame}

@@

	\begin{frame}{ABC MCMC Preliminary Results}
		\includegraphics[height=6cm, width=\textwidth]{distances.jpeg}
	\end{frame}

	\section{Conclusion}
	\begin{frame}{Conclusions}

	\section{Future Work}
	\begin{frame}{Future Work}
